\documentclass[a4paper,10pt]{article}

\usepackage{ucs}
\usepackage[utf8x]{inputenc}
\usepackage[english]{babel}
\usepackage{fontenc}
\usepackage{graphicx}
\usepackage[a4paper, top=2cm]{geometry}

\usepackage[dvips]{hyperref}
\title{String Algorithms 2013 - Assignment 2}
\author{Holger Schmeisky  201211113, Tashi Sherpa, Matus Tomlein}
\date{30.04.2013}

\begin{document}

\maketitle

\subsection*{State of the algorithm}
The algorithm works correctly for all inputs specified on the homepage, and thus we think it works correctly on all inputs.

\subsection*{Insights}
While implementing the algorithm we got a deeper understanding of its working.\\ 
It was very helpful to draw an execution of the algorithm on paper. After we did this, we saw how with the mapping of DFS-traversal numbers to leaf indices, we could very simply calculate the leaf lists of inner nodes as intervals between the DFS-traversal numbers. Before we thought it would be difficult to calculate and store, $LL(n)$ and $LL'(n)$, but with the paper drawing, we saw that after we had traversed all of an inner node's children, we had all the information we needed, to determine the largest subtree (the one with the largest interval) and to store that as interval. In the later iteration through the inner node's leaflist, we could just skip the indices in the $LL(n)$ interval.

\subsection*{Problems}
We did not really face any big problems, after the preliminary observations made on paper. We developed the algorithm by first testing it on small input examples (``abaab'') until it produced the correct leaf lists and repeats there and subsequently fed it with larger inputs. Each of the larger inputs discovered new programming errors, but we were able to get it working relatively quickly on all of the inputs on the homepage.

\clearpage
\subsection*{Evaluation}
\end{document}
